Recent advances of malaria parasites detection systems based on mathematical morphology

### 2017-11-24 Table_sum.tex
Updated conclusion and named-ordered authors in pre-proc and segmentation sections

    Di Ruberto \emph{et al.}, 2002 &
		area closing &
		thresholding + granulometry, watershed  transform &	
		skeleton &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		-
\vspace{0.6cm}
		\\

@@

    Gonzalez-Betancourt \emph{et al.}, 2016  &
    	morphological filter, erosion-reconstruction, dilation-reconstruction, closing &
    	-  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

@@

    Kareem \emph{et al.}, 2012  &
    	dilation, erosion &
    	-  &
    	- &
    	two (infected and noninfected) &
    	Acc=88\% SE=90\% SP=86\% \vspace{0.6cm} \\

@@

    Khan \emph{et al.}, 2014  &
    	- &
    	- &
    	- &
    	two (infected and noninfected) &
    	SE=93\% SP=95\% \vspace{0.6cm} \\

@@

    Romero-Rondon \emph{et al.}, 2016  &
    	opening &
    	marker controlled watershed, erosion  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

@@

    Sheikhhosseini \emph{et al.}, 2013  &
    	- &
    	thresholding + hole filling, opening  &
    	- &
    	two (infected and noninfected) &
    	Acc=97.25\% SE=82.21\% SP=98.02\% \vspace{0.6cm} \\

    Somasekar \emph{et al.}, 2015  &
    	- &
    	fuzzy C-means clustering + erosion, hole filling  &
    	- &
    	two (infected and noninfected) &
    	SE=98\% SP=93.3\% \vspace{0.6cm} \\

>>>>

    Di Ruberto \emph{et al.}, 2002 &
		area closing, opening &
		thresholding + granulometry, watershed  transform &	
		skeleton &
		two (\emph{P.falciparum} infected and noninfected) + three life-cycle-stages &
		-
\vspace{0.6cm}
		\\

@@

    Gonzalez-Betancourt \emph{et al.}, 2016  &
    	morphological filter, erosion-reconstruction, dilation-reconstruction, closing &
    	watershed  transform  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

@@

    Kareem \emph{et al.}, 2011, 2012  &
    	dilation, erosion &
    	-  &
    	- &
    	two (infected and noninfected) &
    	Acc=88\% SE=90\% SP=86\% \vspace{0.6cm} \\

@@

@@

    Romero-Rondon \emph{et al.}, 2016  &
    	dilation, opening &
    	marker controlled watershed, erosion  &
    	- &
    	- &
    	- \vspace{0.6cm} \\

@@

    Sheikhhosseini \emph{et al.}, 2013  &
    	hole filling &
    	thresholding + hole filling, opening  &
    	- &
    	two (infected and noninfected) &
    	Acc=97.25\% SE=82.21\% SP=98.02\% \vspace{0.6cm} \\

    Somasekar \emph{et al.}, 2015  &
    	erosion &
    	fuzzy C-means clustering + erosion, hole filling  &
    	- &
    	two (infected and noninfected) &
    	SE=98\% SP=93.3\% \vspace{0.6cm} \\
